### 2019-01-05 Sections/optimising_the_world.tex
Optimal - bad joke

\subsection{Approximate optimisation}\index{Approximate optimisation}

>>>>

\subsection{An example of a poorly constructed joke}\index{Jokes}

I recall a popular quantum computing joke circulating the internet a number of years ago. It went along the lines of:
\\
\\
\textit{Q: What happens when two quantum computers play chess?}\\
\textit{A: White e3, black resigns.}
\\
\\
This joke is of course based on the assumption that quantum computers can efficiently solve the chess problem, foreseeing the whole game, and knowing the full optimal future gameplay.

However this is a poorly-designed joke, since it has been proven that chess is an \textbf{EXP}-complete problem\footnote{When the game is generalised appropriately to an \mbox{$n\times n$} board, since obviously \textit{any} finite instance of any game can be solved in $O(1)$ time.}, believed to lie outside of \textbf{BQP}. Therefore this is a bad joke and it isn't funny.

However, although quantum computers are unlikely to be able to efficiently play chess \textit{optimally}, there may still be some room for improvement in \textit{approximating} optimal moves, to be discussed next in Sec.~\ref{sec:approx_optim}.

\subsection{Approximate optimisation}\label{sec:approx_optim}\index{Approximate optimisation}
